Mixture Models for Single-Cell Assays with Applications to Vaccine Studies

### 2013-06-25 MIMOSA/mimosafigures/manuscriptFigures.Rmd
update html

Unconstrained MIMOSA fit to data violating model assumptions
-----

@@

#rerun one sided sims at 50K, more than 10 reps
sims.50K<-OneSidedSims(hvtn.result.mcmc,N=50000)
levs<-levels(sims.50K$sim.FDR$method)
levs[1]<-"MIMOSA (one sided)"
sims.50K$sim.FDR$method<-factor(sims.50K$sim.FDR$method,labels=levs)
levs<-levels(sims.50K$sim.ROC$method)
levs[2]<-"MIMOSA (one sided)"
sims.50K$sim.ROC$method<-factor(sims.50K$sim.ROC$method,labels=levs)
p5<-ggplot(subset(sims.50K$sim.FDR,Nobs!=200))+geom_line(aes(x=fdr.hat,y=true.fdr.hat,col=relevel(method,"MIMOSA (one sided)")),direction="vh",lwd=1.5,alpha=0.8)+theme_bw()+scale_x_continuous("Nominal FDR")+scale_y_continuous("Observed FDR")+coord_cartesian(xlim=c(-0.01,1.01),ylim=c(-0.01,1.01))+scale_color_discrete("Method")+facet_wrap(~Nobs)+theme(strip.text.x=element_text(size=18),axis.title.x=element_text(size=18),axis.title.y=element_text(size=18),axis.text.x=element_text(angle=90))+geom_abline(1,lty=3)
p6<-ggplot(subset(sims.50K$sim.ROC,Nobs!=200))+geom_line(aes(x=FPR.hat,y=TPR.hat,col=relevel(method,"MIMOSA (one sided)")),direction="vh",lwd=1.5,alpha=0.8)+theme_bw()+scale_x_continuous("FPR")+scale_y_continuous("TPR")+coord_cartesian(xlim=c(-0.01,1.01),ylim=c(-0.01,1.01))+scale_color_discrete("Method")+facet_wrap(~Nobs)+theme(strip.text.x=element_text(size=18),axis.title.x=element_text(size=18),axis.title.y=element_text(size=18),axis.text.x=element_text(angle=90))
```{r eval=FALSE}
pdf(file="/Users/gfinak/Documents/manuscripts/MIMOSA_Paper/Figures/Sim_OneSided_ROC_varyNobs.pdf",width=9,height=3)
p6
dev.off()
pdf(file="/Users/gfinak/Documents/manuscripts/MIMOSA_Paper/Figures/Sim_OneSided_FDR_varyNobs.pdf",width=8,height=3)
p5
dev.off()
```

### One-sided simulations, 50K events. N=20,50,100

```{r echo=FALSE}
p6
p5
```

>>>>

Unconstrained MIMOSA fit to data violating model assumptions
-----
Top row shows results for MIMOSA fit to data simulated from a model violating model assumptions.
Bottorm row shows results of two-sided MIMOSA fit to data with low counts (10K events).

@@

#rerun one sided sims at 50K, more than 10 reps
sims.50K<-OneSidedSims(hvtn.result.mcmc,N=50000)
levs<-levels(sims.50K$sim.FDR$method)
levs[1]<-"MIMOSA (one sided)"
sims.50K$sim.FDR$method<-factor(sims.50K$sim.FDR$method,labels=levs)
levs<-levels(sims.50K$sim.ROC$method)
levs[2]<-"MIMOSA (one sided)"
sims.50K$sim.ROC$method<-factor(sims.50K$sim.ROC$method,labels=levs)

```{r eval=TRUE}
p5<-ggplot(subset(sims.50K$sim.FDR,Nobs!=200))+geom_line(aes(x=fdr.hat,y=true.fdr.hat,col=relevel(method,"MIMOSA (one sided)")),direction="vh",lwd=1.5,alpha=0.8)+theme_bw()+scale_x_continuous("Nominal FDR")+scale_y_continuous("Observed FDR")+coord_cartesian(xlim=c(-0.01,1.01),ylim=c(-0.01,1.01))+scale_color_discrete("Method")+facet_wrap(~Nobs)+theme(strip.text.x=element_text(size=18),axis.title.x=element_text(size=18),axis.title.y=element_text(size=18),axis.text.x=element_text(angle=90))+geom_abline(1,lty=3)
p6<-ggplot(subset(sims.50K$sim.ROC,Nobs!=200))+geom_line(aes(x=FPR.hat,y=TPR.hat,col=relevel(method,"MIMOSA (one sided)")),direction="vh",lwd=1.5,alpha=0.8)+theme_bw()+scale_x_continuous("FPR")+scale_y_continuous("TPR")+coord_cartesian(xlim=c(-0.01,1.01),ylim=c(-0.01,1.01))+scale_color_discrete("Method")+facet_wrap(~Nobs)+theme(strip.text.x=element_text(size=18),axis.title.x=element_text(size=18),axis.title.y=element_text(size=18),axis.text.x=element_text(angle=90))
```{r eval=FALSE}
pdf(file="/Users/gfinak/Documents/manuscripts/MIMOSA_Paper/Figures/Sim_OneSided_ROC_varyNobs.pdf",width=9,height=3)
p6
dev.off()
pdf(file="/Users/gfinak/Documents/manuscripts/MIMOSA_Paper/Figures/Sim_OneSided_FDR_varyNobs.pdf",width=8,height=3)
p5
dev.off()
```
